### 2019-04-23 paper.tex
Start from copy of PDPTA 2018 paper with rewritten Abstract and Introduction.

%\documentclass[twocolumn,letterpaper]{article}
\documentclass[10pt]{csce}

\usepackage[hmargin=.75in,vmargin=1in]{geometry}
\usepackage[american]{babel}
\usepackage[T1]{fontenc}
\usepackage{times}
\usepackage{caption}
\usepackage{flushend}

\usepackage{gensymb,hyperref,graphicx,paralist,amsmath,multirow}
\usepackage[table]{xcolor}
\pagenumbering{gobble}

\title{\bf A Model-Based Scheduling Framework for Enhancing Robustness}

%%%% Make sure the author names are boldface.
\author{
{\bfseries Nicolas Grounds and John K. Antonio}\\
School of Computer Science, University of Oklahoma, Norman, Oklahoma, United States of America\\
}

\begin{document}

\maketitle                        %%%% To set Title and Author names.

\begin{abstract}
In previous work the performance of scheduling algorithms for dynamic
scheduling of tasks in a distributed system were evaluated for their
robustness to error in the model of tasks' information.  There it was
found that incorporating task completion timings from the actual distributed
system into the algorithms' model of the system was crucial for achieving
robustness.  In this paper, various degrees of feedback, rather than simply
all-or-none, are evaluated using the same simulated studies as in previous
work and a proposed strategy for biasing model tasks' information is proposed
in order to counteract the most egregious effects of model error on
performance.
\end{abstract}

\vspace{1em}
\noindent\textbf{Keywords:}
 {\small distributed system, scheduling, performance, robustness, biasing}

\section{Introduction and Background}
\label{sec:Intro}

Scheduling computational tasks to machines so as to improve specified metrics
of performance has been the topic of a plethora of good work produced over the
past several decades \cite{taxonomy}. The underlying assumptions and objectives
of this body of work varies along several dimensions. First, some work assumes
all tasks are independent whereas other work, as in this paper, allows for
tasks to have dependency or precedence relationships with other tasks (for
which interrelated tasks are typically represented in a directed acyclic graph,
or DAG). Additionally, there are static formulations to scheduling in which a
desired schedule is detemined offline based on assumed knowledge related to the
machines' available resources and, correspondingly, the resource requirements
of the computational tasks.

Conversely, this paper addresses dynamic scheduling in which the schedule for
tasks is determined online in real-time with the execution of those tasks on a
distributed system. Unlike the static scheduling problem, dynamic scheduling
does not require upfront knowledge of the arrival of future tasks into the
system for scheduling. Algorithms for dynamic scheduling make use of knowledge
about the tasks which are ready for scheduling and their resource requirements
such as CPU and memory load as well as the resource capacities of the machines
in the distributed system.

Such algorithms for dynamic scheduling may be based on heuristics for selecting
which tasks to prioritize execution of and determining when to begin their
execution and on which machine. Other algorithms may actively attempt to
optimize scheduling decisions with respect to a desired outcome based on a
user-defined objective.  Both types of algorithms are generally measured
and compared to one another against such objectives such as minimizing makespan
(time required for completed execution of all tasks) \cite{stochastic}, or, as
in this paper, the degree to which all tasks of a DAG are completed by a
DAG-associated deadline.

Scheduling algorithms may orthogonally be evaluated based on their robustness,
for example, how well the same objective is achieved when information provided
to the scheduling algorithm contains errors such as inaccuracies in the
amount of resource requirements of the tasks.  In previous work \cite{pdpta18}
four dynamic scheduling algorithms' robustness to error with respect to
performance against an objective of completing DAGs before their deadline was
presented, showing how some algorithms were not robust to even the smallest
amount of simulated error.  Additionally, the use of task completion time
feedback from the actual distributed system back into the modeled system used
by the scheduling algorithms was found to substantially improve robustness of
all four scheduling algorithms to even large amounts of simulated error.

The remainder of the paper is organized in the following manner.  Section
\ref{sec:Framework} describes the problem domain and the simulation software's
use of modeling the distributed system where errors in task requirements may
be inherent.  Section \ref{sec:Biasing} presents an approach to counteracting
model error to prevent scheduling algorithms from over-committing system
resources to executing too many tasks concurrently. Section \ref{sec:Results}
presents results of simulated case studies within that software simulator.
Finally, Section \ref{sec:Summary} summarizes the findings from these
simulations and presents the conclusions of our work.

\section{Problem Domain and Simulation Environment}
\label{sec:Framework}

The present work is a meta-approach that is motivated by the desire to apply
existing scheduling approaches within a framework that is realistic and
operationally practical.  In terms of scheduling taxonomy, we assume a dynamic
scheduling formulation in which the computational jobs (we call them workflows)
are modeled as directed acyclic graphs, i.e., the tasks of a workflow have
precedence constraints.  Furthermore, each workflow (not individual tasks) is
endowed with a deadline.

Our framework, illustrated in Figure \ref{fig:platform}, consists of one
centralized scheduler and two instances of the computational platform.  The
first instance, denoted as the actual platform, represents the actual machines
(virtual or physical) upon which the actual workflows' tasks are to be executed.
The second instance of the platform, denoted as the model platform, is a
mathematical and/or simulated model representation of the actual platform.  The
scheduler component makes decisions about what machine each task is to be
executed on and when (at or after all the tasks precedence constraints are
satisfied) that execution should begin.  The scheduler makes use of a scheduling
algorithm, which requires some model of the workflows' tasks' requirements.
Scheduling decisions are implemented by a task assigner particular to the
platform, model or actual.

\begin{figure}
	\begin{center}
		\includegraphics[angle=-90,width=0.5\textwidth]{figures/PlatformDiagram.pdf}
	\end{center}
	\caption{Block diagram illustrating proposed framework.}
	\label{fig:platform}
\end{figure}

Much past research has focused on the scheduler component of Figure
\ref{fig:platform}; building schedulers to achieve enhanced performance and/or
robustness.  This is often achieved by focusing on the modeled workflow's
rquirements information provided to the scheduler.  In addition to modeling
requirements, our framework also emphasizes modeling of the platform resources
through the model platform component, providing additional opportunities for
research and improvement.  Such improvements can be realized by building more
accurate models or by making use of feedback from the actual platform to correct
the model platform, indicated by the dashed line of Figure \ref{fig:platform}.

Development and evaluation of static schedules, and schedulers, make use of the
components below the dotted line to build a schedule (set of scheduling
decisions for where and when each task should be executed).  That static
schedule is then used by the actual task assigner component, e.g., via a lookup
table, in a running system like that represented above the dotted line.  Also,
for scheduling algorithms that require training, or offline optimization of
parameters, the same components below the dotted line would be used prior to
deployment of the algorithm in the scheduler of a live system, represented
by the components above the dashed-dotted line.

In the ideal case that the model components match the behavior of the
corresponding actual components, feedback from the actual platform is
unnecessary. Realistically, however, the model components will have deviations
(or errors) in comparison to the actual components with how they
model the tasks' requirements and the availability of platform resources.  This
leads to erroneous information being presented to the scheduler that can be
summarized as two interrelated types.  First, task requirement error results in
inaccurate information about resource load in the model platform, which is
utilized by the scheduler.  Because all scheduling algorithms must fundamentally
determine when to schedule additional tasks on already-loaded resources versus
when to delay starting new tasks until some already-running tasks complete and
the load of the resources lightens (increasing its efficiency), an algorithm
given wrong information about resource load will generally make poor
decisions.

The second type of error the model may exhibit is in the representation of
how much work a task requires to be completed before the task is considered
finished.  When a model's error causes a task's work requirement to be
underestimated, it can lead the scheduling algorithm to assign additional
work to the resource modeled as now having a lightened load.  In this scenario
the error compounds if the algorithm assigns new tasks to the resource because
the additional load causes the atual system's resource to become even less
efficient, further diverging the model from the actual system and causing the
task erroneously modeled as finished to take even longer to finish in the
actual system.  It is also possible that the model for a task overestimates
the task's work requirement in which case the model of the resource remains
loaded while the actual system's resource may be idle.

To counteract the effect of the model diverging from the actual system in
terms of knowledge of which tasks are running, the model may be improved
using feedback from the actual system regarding task completion.  A simple
implementation of this feedback in practice is to instrument the actual system
to provide periodic information about the running tasks on each system
resource.  However, this can cause the model to `lag' behind the actual system
if modeled tasks are not considered completed until a periodic check reveals
its actual system counterpart is no longer executing.  Because scheduling
algorithms make decisions once the state of the system changes in response to
tasks finishing, the aforementioned `lag' may be avoided by having the actual
system provide event-based feedback upon completion of each task.  This latter
`event-driven' approach is adopted in our framework.

\section{Use of Biasing}
\label{sec:Biasing}

This section presents simulated results of the outcomes of scheduling algorithms
whose decisions are made based on a model platform of the (simulated) actual
system in which error is introduced in one aspect of the workflows' tasks'
requirements.  It is shown that by using actual task completion events (fed back
from the actual platform) to correct inaccuracies present in the model
platform, all scheduling algorithms analyzed become very robust to errors in the
tasks' requirements considered.

All simulations were performed using simulator software developed for
previous research \cite{costmin} and made publically available as open source
\cite{soasim}.  As in \cite{costmin} workflows are defined as a directed
acyclic graph where graph nodes represent the computational tasks which are
individually schedulable to execute on one of the platform's available machines.
Graph edges represent precedence constraint where one task must complete
execution before the connected task is able to be scheduled and begin
execution.  In every simulation a scheduling algorithm
is used to schedule tasks from arriving workflows of one of three types, as
also defined in \cite{costmin}: small workflows representative of simple
interactive application jobs, medium workflows representative of web services
jobs, and large workflows representative of large-scale batch-oriented jobs.
Various workflow and task characteristics are summarized in Table
\ref{tab:params}.

\begin{table}
	\begin{tabular}{|l|c|c|c|}
		\hline
		\textbf{Parameter}	& \textbf{Small}	& \textbf{Medium}	& \textbf{Large} \\
		\hline
		Total tasks				& [5,16]	& [10,72]	& [45,800] \\
		Potential Task Parallelism	& [1,2]	& [2,3]		& [5,20] \\
		Task CPU cycles (work)	& [1,2.5]	& [10,50]	& [50,175] \\
		Task CPU utilization	& [0.5,1]	& [0.5,1]	& [0.5,1] \\
		Task memory footprint	& [0.05,0.15] & [0.05,0.1] & [0.05,0.1] \\
		\hline
	\end{tabular}
	\caption{Table of basic workflow (DAG) sizes and tasks' requirements by
		workflow type.}
	\label{tab:params}
\end{table}

As part of the simulation studies the model workflows are given task
requirements where the tasks' amount of CPU cycles ($C_M$) to be completed has
an error term applied to it with respect to the actual value ($C_A$).
This error term parameter $X$ is varied between experiments from 0.001 to 0.9.

\begin{equation}
\begin{split}
C_M & \leftarrow (1+x)C_A \\
x & \in [-X,X]
\end{split}
\end{equation}

\noindent The values for $x$ drawn from $[-X,X]$ assume a uniform distribution.

As with \cite{costmin} all simulations used a simulated platform of 16 machines
with the same resource capacities: $4$ CPUs and a normalized memory capacity of
$1.0$.  From Table \ref{tab:params}, then, each task would consume between half
and all of a single CPU and between $5\%$ and $15\%$ (for small workflows, or
$10\%$ for medium and large) of total memory.  For all numeric results for
$10\%$ for medium and large) of total memory.  Platform machine efficiency was
simulated the same as in \cite{costmin} where cumulative CPU load of all
executing tasks on a machine, $\ell_c$, resulted in an effiency, $e_c$ given in
Eq. \ref{eq:cpueff}.  Memory effiency, $e_m$, based on cumulative memory
load of all executing tasks, $\ell_m$, is given in Eq. \ref{eq:memeff}.
The combined efficiency, $e = e_c e_m$, represents the amount of work
accomplished on each executing task per unit of time.

\begin{equation}
\label{eq:cpueff}
e_c = \begin{cases}
	1, ~~~~~~~~\ell_c < 4 \\
	(4/\ell_c), ~~\ell_c \ge 4
\end{cases}
\end{equation}

\begin{equation}
\label{eq:memeff}
e_m = \frac{10}{10 + \frac{1}{(1/\ell_m) - 1}}
\end{equation}

For all numeric results for
performance the value presented is an averaged value across ten simulations
where the workflows and tasks were the same but a unique random error term,
$x$, was used for each model task's required CPU cycles.

\begin{figure*}
	\begin{center}
		\includegraphics[width=0.9\textwidth,height=3in]{figures/Histogram_All_NoLoss_NoBias_LowError.pdf}
	\end{center}
	\caption{Histogram of workflows by normalized tardiness comparing
		relative performance of scheduling algorithms with no error (vertical
		bars) and with 0.1\% error applied to the model of the workflow
		requirements (line graphs).  In this scenario, task completion event
		feedback was \textbf{not} employed to correct the model platform.}
	\label{fig:noloss-lowerror-nofeedback}
\end{figure*}

\section{Results}
\label{sec:Results}

Figure \ref{fig:noloss-lowerror-nofeedback} shows the performance of scheduling
algorithms and the significant performance impact that even a small amount of
error has.  In this figure as with prior research, performance is depicted
visually as a histogram of the number of workflows completed in intervals based
on their normalized tardiness (the time difference between the completion and
the target deadline normalized by on-time completion time of the workflow).
In this representation a normalized tardiness of 0 represents a workflow that
completed exactly at its deadline, negative values represent workflows completed
before their deadline, and positive values those completed late.

The histogram bars of Figure \ref{fig:noloss-lowerror-nofeedback} represent the
performance of scheduling algorithms under the ideal circumstance of no error
in the model (i.e., the model platform perfectly predicts and represents the
resources required by a task and its execution completion time).  These
histogram bar results demonstrate how CMSA with either of the two
cost functions (Sigmoid or Quadratic) completes the largest majorities of
workflows ahead of their deadline.  The PLLF (proportional least laxity first)
algorithm completes workflows up to 4 times later (as a proportion of the
ideal finish time) than the deadline. The FCFS (first-come, first-serve)
algorithm performs relatively poorly with workflows completing far later than
their deadline because it is oblivious to deadlines and therefore often will
put off scheduling tasks of a recently-arrived workflow with a `tight' deadline
by prioritizing a less-recently arrived workflow despite its deadline being
further into the future and possibly more relaxed.

The lines graphed in Figure \ref{fig:noloss-lowerror-nofeedback} represent the
same algorithms' histogram of workflow completion in the presence of 0.1\% error
in the model platform.  As depicted, one algorithm (CMSA algorithm optimizing
the cost based on a Sigmoid cost function) maintains roughly the same
performance in the presence of this small model error, as without it.  All three
other algorithms exhibit a dramatic loss in performance, i.e., a shift of many
workflows completing ahead of or shortly after their deadline to completing
many times over later than their deadline.  In this scenario, completion events
were \textbf{not} employed to correct the model platform.

\begin{table}
       \begin{center}
       \begin{tabular}{lllll}
\textbf{Error, }$X$ & \textbf{CMSA}	& \textbf{CMSA}				& \textbf{FCFS}				& \textbf{PLLF} \\
		& \textbf{(Quad)}			& \textbf{(Sig)}			&							& \\
0.0		& \cellcolor{red! 6}16.54	& \cellcolor{green!9}1.77	& \cellcolor{red!28}38.49	& \cellcolor{red!28}38.72 \\
0.001	& \cellcolor{red!20}30.52	& \cellcolor{green!9}1.92	& \cellcolor{red!51}61.39	& \cellcolor{red!40}50.96 \\
0.005	& \cellcolor{red!24}34.75	& \cellcolor{green!9}1.84	& \cellcolor{red!49}59.48	& \cellcolor{red!42}52.39 \\
0.01	& \cellcolor{red!20}30.86	& \cellcolor{green!7}2.99	& \cellcolor{red!50}60.35	& \cellcolor{red!39}49.39 \\
0.05	& \cellcolor{red!18}28.87	& \cellcolor{green!1}8.99	& \cellcolor{red!53}63.60	& \cellcolor{red!39}49.54 \\
0.1		& \cellcolor{red!22}32.11	& \cellcolor{red! 5}15.60	& \cellcolor{red!50}60.77	& \cellcolor{red!42}52.65 \\
0.5		& \cellcolor{red!24}34.34	& \cellcolor{red!14}24.96	& \cellcolor{red!42}52.85	& \cellcolor{red!45}55.68 \\
0.9		& \cellcolor{red!22}32.93	& \cellcolor{red!16}26.12	& \cellcolor{red!44}54.36	& \cellcolor{red!48}58.64 \\
       \end{tabular}
       \caption{Percent of workflows late for four scheduling algorithms
			across various amounts of error in the model platform.  Completion
			events were \textbf{not} employed to correct the model platform.}
       \label{tab:perclate}
       \end{center}
\end{table}

Table \ref{tab:perclate} lists the value of percent of all workflows completed
late (after their deadline) as a single performance metric for the scheduling
algorithms across various amounts of the error term, $X$.  This metric (percent
late workflows) is useful in comparing the impact of increasing error on the
performance of each scheduling algorithm.  Like Figure
\ref{fig:noloss-lowerror-nofeedback}, it illustrates how CMSA (with sigmoid cost
function) is robust to small error, whereas the other algorithms are not.  It
also shows that while the performance of CMSA (Sig) degrades as error increases,
the other three algorithms maintain nearly a constant level of even poorer
performance with any amount of error.  These results show how some algorithms
(CMSA with Sigmoid cost function) can be relatively robust (at least with
respect to this performance metric) for small amounts of error but how all
algorithms eventually perform poorly when using a model platform that fails to
reasonably represent the actual system.

The model task requirement with respect to the amount of CPU cycles each task
requires has a compounding effect when the model system declares, erroneously,
that a task has completed (ahead of the actual system) and thus the scheduler
determine to begin execution of an additional task that increases the system
resource load in the actual system and slows the progression toward completion
even further.  Intuitively, this compounding error is most likely the reason
for such a dramatic decrease in overall scheduler performance for the three
affected algorithms of Figure \ref{fig:noloss-lowerror-nofeedback}.

\begin{figure*}
	\begin{center}
		\includegraphics[width=0.9\textwidth,height=3in]{figures/Histogram_All_NoLoss_NoBias_HighErrorWithoutModelFinishEvents.pdf}
	\end{center}
	\caption{Histogram of workflows by normalized tardiness comparing relative
		performance of scheduling algorithms with no error (vertical bars) and
		with 90\% error applied to the model of the workflow requirements
		(line graphs).  In this scenario, task completion event feedback
		\textbf{was} employed to correct the model platform.}
	\label{fig:noloss-higherror-nomodel}
\end{figure*}

The strategy proposed in this paper is to incorporate feedback from the actual
platform for task completions as an event-based trigger for updating the
model platform and allowing the scheduler to schedule new tasks.  Figure
\ref{fig:noloss-higherror-nomodel} depicts results of the performance of
scheduling algorithms comparable with Figure
\ref{fig:noloss-lowerror-nofeedback} except that the error introduced in the
model is much higher (90\%, instead of 0.1\%) and the model platform uses task
completion events from the actual platform (instead of relying on the model
platform estimates of task completions).  Given that the line graphs match
much more closely to the vertical bars than in Figure
\ref{fig:noloss-lowerror-nofeedback}, this illustrates how even for large
model error the incorporation of actual platform task completion feedback
increases the robustness of all four scheduling algorithms.  The CMSA (Sig)
algorithm which was robust for small amounts of error, as well as the other
three algorithms which were not robust even for the smallest amount of error
studied (0.1\%) all achieve nearly the same level of performance (i.e. shape
of histogram) as with having a perfect, no-error model.

\section{Summary and Future Work}
\label{sec:Summary}

In this paper we introduced a framework for understanding and evaluating
scheduling algorthms' performance and robustness with
respect to error in tasks' resource requirements.  This framework
incorporates a model of the actual system in which errors and uncertainties can
be represented.  Through simulation studies we examined the performance of four
scheduling algorithms and the impact of error in the model system upon their
performance.  While the CMSA algorithm (using a sigmoid cost function) had some
degree of robustness, i.e. it was able to achieve similar performance in the
presence of very small error, all algorithms exhibited poor performance with
even moderate amounts of error present in one dimension of the model workflows
requirements (CPU cycles required for the tasks).

We also introduced and simulated the notion of incorporating feedback from
the actual system back into the model system.  Through simulation studies we
showed how all algorithms can benefit from feedback of task completion events
and thus become relatively robust to even substantial error in the model
system.

In the present paper, we assumed that tasks' completion events are detected
and fed back in order to `correct' the model platform.  Under this
assumption, the model completely relies on actual completion events being
fed back.  Future work will consider the possibility in which partial feedback
(of some) completion events are available and fed back to the model.  This
`partial feedback' assumption may be more practical than the complete feedback
used in this paper in situations where there would be significant overhead
instrumenting the actual system so as to feed back each and every completion
event.  In such cases, taking small samplings of completion events from the
actual system would be more practical. Finally, future work will also
investigate the effect of non-uniform error and/or error distributions without
an expected value of $0$.

\bibliography{paper}{}
\bibliographystyle{unsrt}

\end{document}

### 2019-04-26 paper.tex
Draft complete sections 2 and 3 and start on Results section 4.  Add illustration material for bias visualizations.

@@
 
-The present work is a meta-approach that is motivated by the desire to apply
-existing scheduling approaches within a framework that is realistic and
-operationally practical.  In terms of scheduling taxonomy, we assume a dynamic
-scheduling formulation in which the computational jobs (we call them workflows)
-are modeled as directed acyclic graphs, i.e., the tasks of a workflow have
-precedence constraints.  Furthermore, each workflow (not individual tasks) is
-endowed with a deadline.
+The present work is an extension to previous work \cite{pdpta18} in which a
+model-based approach to dynamically scheduling tasks from DAGs (called
+workflows) was introduced.  Four scheduling algorithms were tested in a
+simulation environment \cite{soasim} given the same 24-hour simulated period
+of arriving workflows ranging in size from 5 tasks up to 800.  Each workflow
+had a known, predetermined deadline and scheduling algorithms were evaluated
+based both on the number of workflows completed before their deadline and the
+distribution of workflow counts completed at various normalized proportions
+past their deadline (e.g., workflows up to 100\% late relative to the amount
+of time between their arrival and deadline).
 
-Our framework, illustrated in Figure \ref{fig:platform}, consists of one
-centralized scheduler and two instances of the computational platform.  The
-first instance, denoted as the actual platform, represents the actual machines
-(virtual or physical) upon which the actual workflows' tasks are to be executed.
-The second instance of the platform, denoted as the model platform, is a
-mathematical and/or simulated model representation of the actual platform.  The
-scheduler component makes decisions about what machine each task is to be
-executed on and when (at or after all the tasks precedence constraints are
-satisfied) that execution should begin.  The scheduler makes use of a scheduling
-algorithm, which requires some model of the workflows' tasks' requirements.
-Scheduling decisions are implemented by a task assigner particular to the
-platform, model or actual.
+Scheduling algorithms are used to determine from a given queue of tasks
+ready to begin executing (i.e. tasks of arrived workflows that have no
+precedence constraints or whose precedent tasks have all completed) both
+when the task should begin executing and on which machine of the platform.
+Unlike some scheduling research, tasks are permitted to executing concurrently
+with other tasks on the same machine which increases machines' overall load
+on resources such as CPU and memory and thereby slows the rate of work on each
+executing task.  Original work in \cite{pdpta09} details this non-linear
+degradation of rate of work (efficiency) due to concurrent task execution.
+
+Figure \ref{fig:platform} illustrates the various components and general
+flow of information within the model-based approach to executing and evaluating
+scheduling algorithms.  Whereas the modeled tasks' requirements (CPU load,
+required number of CPU cycles, and memory load) may contain errors relative to
+the true values of those tasks, the model platform may diverge from the
+actual platform in terms of which tasks are completed and which are still
+executing.
 
@@
 	\end{center}
-	\caption{Block diagram illustrating proposed framework.}
+	\caption{Block diagram illustrating model-based framework from
+		\cite{pdpta18}.}
 	\label{fig:platform}
@@
 
-Much past research has focused on the scheduler component of Figure
-\ref{fig:platform}; building schedulers to achieve enhanced performance and/or
-robustness.  This is often achieved by focusing on the modeled workflow's
-rquirements information provided to the scheduler.  In addition to modeling
-requirements, our framework also emphasizes modeling of the platform resources
-through the model platform component, providing additional opportunities for
-research and improvement.  Such improvements can be realized by building more
-accurate models or by making use of feedback from the actual platform to correct
-the model platform, indicated by the dashed line of Figure \ref{fig:platform}.
+All four studied scheduling algorithms were shown to be sensitive to
+even small amounts of error in modeled tasks.  Each scheduling algorithm
+exhibited a decreased percent of workflow completed ahead of their deadline
+with the smallest amount of error studied.  For three of the scheduling
+algorithms the decrease was substantial, but relatively equal, regardless of
+the amount of error.  For the fourth scheduling algorithm, the decrease was
+less severe overall and was propotionate to the amount of error.  The
+fourth algorithm was thus declared to be somewhat robust to small amounts of
+error (less than 0.5\%) but ultimately, like all three others, was not
+robust for errors of 1\% or greater.
 
-Development and evaluation of static schedules, and schedulers, make use of the
-components below the dotted line to build a schedule (set of scheduling
-decisions for where and when each task should be executed).  That static
-schedule is then used by the actual task assigner component, e.g., via a lookup
-table, in a running system like that represented above the dotted line.  Also,
-for scheduling algorithms that require training, or offline optimization of
-parameters, the same components below the dotted line would be used prior to
-deployment of the algorithm in the scheduler of a live system, represented
-by the components above the dashed-dotted line.
+The main result of \cite{pdpta18} showed that incorporating feedback of
+task completions from the actual platform to the model platform thereby
+preventing the model platform from modeling a task completing before the
+actual task completed dramatically increased robustness of all scheduling
+algorithms for even errors up to 90\% (the highest amount studied).  Figure
+\ref{fig:underestimating} illustrates why the model platform underestimating
+the requirements of a task and thereby modeling it as completed ahead of the
+actual task can be so detrimental.
 
-In the ideal case that the model components match the behavior of the
-corresponding actual components, feedback from the actual platform is
-unnecessary. Realistically, however, the model components will have deviations
-(or errors) in comparison to the actual components with how they
-model the tasks' requirements and the availability of platform resources.  This
-leads to erroneous information being presented to the scheduler that can be
-summarized as two interrelated types.  First, task requirement error results in
-inaccurate information about resource load in the model platform, which is
-utilized by the scheduler.  Because all scheduling algorithms must fundamentally
-determine when to schedule additional tasks on already-loaded resources versus
-when to delay starting new tasks until some already-running tasks complete and
-the load of the resources lightens (increasing its efficiency), an algorithm
-given wrong information about resource load will generally make poor
-decisions.
+\begin{figure}
+	\begin{center}
+		\includegraphics[width=0.5\textwidth]{figures/UnderestimatedErrorEffect_ModelTaskWork.pdf}
+		\includegraphics[width=0.5\textwidth]{figures/UnderestimatedErrorEffect_ActualTaskWork.pdf}
+	\end{center}
+	\caption{Illustrating the disconnect due to error such that model task
+		requirements underestimate actual task requirements and the model
+		task finishes ahead of the actual task.}
+	\label{fig:underestimating}
+\end{figure}
 
-The second type of error the model may exhibit is in the representation of
-how much work a task requires to be completed before the task is considered
-finished.  When a model's error causes a task's work requirement to be
-underestimated, it can lead the scheduling algorithm to assign additional
-work to the resource modeled as now having a lightened load.  In this scenario
-the error compounds if the algorithm assigns new tasks to the resource because
-the additional load causes the atual system's resource to become even less
-efficient, further diverging the model from the actual system and causing the
-task erroneously modeled as finished to take even longer to finish in the
-actual system.  It is also possible that the model for a task overestimates
-the task's work requirement in which case the model of the resource remains
-loaded while the actual system's resource may be idle.
+In Figure \ref{fig:underestimating} two tasks, $t_1$ and $t_2$, both have
+the same amount of CPU cycles, $C$, required for their completion.  In the
+top half is the modeled platform's view of time in which task $t_1$ begins
+executing first and when it completed, $t_2$ is scheduled to immediately
+begin executing.  However, because the modeled requirements of $t_1$ were
+an underestimate of the actual $t_1$'s requirements, when the model of
+$t_1$ finishes and $t_2$ is scheduled to begin, the actual platform is not
+yet finished with $t_1$ and thus must work concurrently on $t_1$ and $t_2$
+for some time until the actual $t_1$ task does complete.  This causes both
+$t_1$ and $t_2$ to have actual completion times later than the modeled
+completion times because of the unintentionally-overallocated resources of
+the machine executing the tasks.  By extension, if another task, say $t_3$,
+were to be scheduled to begin after $t_2$ finishes this problem could compound
+because $t_2$'s actual completion would delayed by concurrent execution with
+$t_1$ and further delayed by concurrent execution with $t_3$.
 
-To counteract the effect of the model diverging from the actual system in
-terms of knowledge of which tasks are running, the model may be improved
-using feedback from the actual system regarding task completion.  A simple
-implementation of this feedback in practice is to instrument the actual system
-to provide periodic information about the running tasks on each system
-resource.  However, this can cause the model to `lag' behind the actual system
-if modeled tasks are not considered completed until a periodic check reveals
-its actual system counterpart is no longer executing.  Because scheduling
-algorithms make decisions once the state of the system changes in response to
-tasks finishing, the aforementioned `lag' may be avoided by having the actual
-system provide event-based feedback upon completion of each task.  This latter
-`event-driven' approach is adopted in our framework.
+The previous example illustrates why allowing the model to platform to
+inform scheduling algorithms when tasks are complete and machines are
+idle (or less loaded) in the presense of error which may underestimate tasks'
+true requirements can be so detrimental.  With feedback of every task's
+completion from the actual platform the modeled completion times of tasks
+may be safely ignored.  However, complete feedback of all tasks' completion
+may be impractical in a live system, or may simply be cost-prohibitive.
+This paper thus seeks to address the question of whether partial feedback
+of tasks' completion times may be sufficient to achieve some level of
+robustness to model error.  In addition, based specifically on the
+knowledge of the underestimating problem illustrated prior, in Section
+\ref{sec:Biasing} that follows a specific approach to counteracting
+that problem by biasing model task requirements is proposed.  Results of
+both partial feedback and biasing are presented in Section \ref{sec:Results}.
 
-\section{Use of Biasing}
+\section{Biasing Model Requirements}
 \label{sec:Biasing}
 
-This section presents simulated results of the outcomes of scheduling algorithms
-whose decisions are made based on a model platform of the (simulated) actual
-system in which error is introduced in one aspect of the workflows' tasks'
-requirements.  It is shown that by using actual task completion events (fed back
-from the actual platform) to correct inaccuracies present in the model
-platform, all scheduling algorithms analyzed become very robust to errors in the
-tasks' requirements considered.
+As illustrated in Figure \ref{fig:underestimating}, if the model task
+requirements are an underestimate of the actual task's requirements then
+scheduling algorithms may schedule future tasks to begin executing
+unintentionally-concurrent with other tasks, delaying their completion.
+However, if the model is known to have error which may underestimate
+task requirements, then the model task requirements could simply be
+biased by increasing its value in order to reduce (or ideally, eliminate)
+the probability that it underestimates the actual task requirements.
+In this section three proposed strategies for biasing model task
+requirements are proposed.
 
-All simulations were performed using simulator software developed for
-previous research \cite{costmin} and made publically available as open source
-\cite{soasim}.  As in \cite{costmin} workflows are defined as a directed
-acyclic graph where graph nodes represent the computational tasks which are
-individually schedulable to execute on one of the platform's available machines.
-Graph edges represent precedence constraint where one task must complete
-execution before the connected task is able to be scheduled and begin
-execution.  In every simulation a scheduling algorithm
-is used to schedule tasks from arriving workflows of one of three types, as
-also defined in \cite{costmin}: small workflows representative of simple
-interactive application jobs, medium workflows representative of web services
-jobs, and large workflows representative of large-scale batch-oriented jobs.
-Various workflow and task characteristics are summarized in Table
-\ref{tab:params}.
-
-\begin{table}
-	\begin{tabular}{|l|c|c|c|}
-		\hline
-		\textbf{Parameter}	& \textbf{Small}	& \textbf{Medium}	& \textbf{Large} \\
-		\hline
-		Total tasks				& [5,16]	& [10,72]	& [45,800] \\
-		Potential Task Parallelism	& [1,2]	& [2,3]		& [5,20] \\
-		Task CPU cycles (work)	& [1,2.5]	& [10,50]	& [50,175] \\
-		Task CPU utilization	& [0.5,1]	& [0.5,1]	& [0.5,1] \\
-		Task memory footprint	& [0.05,0.15] & [0.05,0.1] & [0.05,0.1] \\
-		\hline
-	\end{tabular}
-	\caption{Table of basic workflow (DAG) sizes and tasks' requirements by
-		workflow type.}
-	\label{tab:params}
-\end{table}
-
-As part of the simulation studies the model workflows are given task
-requirements where the tasks' amount of CPU cycles ($C_M$) to be completed has
-an error term applied to it with respect to the actual value ($C_A$).
-This error term parameter $X$ is varied between experiments from 0.001 to 0.9.
+The simplest form of biasing would be to add a constant value to each
+task requirement.  If the maximum magnitude of error for which a model
+task requirement may underestimate the actual task requirement is known,
+then that value would be the ideal bias constant value because it would
+eliminate the model from ever underestimating task requirements but
+bound the worst overestimate to the smallest amount possible for such a
+constant value biasing strategy.  Practically, the maximum error magnitude
+is unlikely to be known, though because it is the most ideal circumstance
+for biasing it is included here and in simulated results of Section
+\ref{sec:Results}.  The equation for a simple constant bias value, $C$,
+addition to each model task requirement, $\hat{X}$, to yield a biased
+model task requirement, $\hat{X^b}$, is given in Eq.
+\ref{eq:cbias}.
 
 \begin{equation}
-\begin{split}
-C_M & \leftarrow (1+x)C_A \\
-x & \in [-X,X]
-\end{split}
+\hat{X^b} \xleftarrow{c} \hat{X} + C
+\label{eq:cbias}
 \end{equation}
 
-\noindent The values for $x$ drawn from $[-X,X]$ assume a uniform distribution.
-
-As with \cite{costmin} all simulations used a simulated platform of 16 machines
-with the same resource capacities: $4$ CPUs and a normalized memory capacity of
-$1.0$.  From Table \ref{tab:params}, then, each task would consume between half
-and all of a single CPU and between $5\%$ and $15\%$ (for small workflows, or
-$10\%$ for medium and large) of total memory.  For all numeric results for
-$10\%$ for medium and large) of total memory.  Platform machine efficiency was
-simulated the same as in \cite{costmin} where cumulative CPU load of all
-executing tasks on a machine, $\ell_c$, resulted in an effiency, $e_c$ given in
-Eq. \ref{eq:cpueff}.  Memory effiency, $e_m$, based on cumulative memory
-load of all executing tasks, $\ell_m$, is given in Eq. \ref{eq:memeff}.
-The combined efficiency, $e = e_c e_m$, represents the amount of work
-accomplished on each executing task per unit of time.
+A more practical approach biasing model task requirements is to assume a bound,
+not on the magnitude of error, but on the fraction or percentage of error.  It
+may be possible, for example, through analysis of past executions of tasks and
+workflows, to estimate the maximum percentage of error for each model task
+requirement, $\hat{X}$, relative to the actual task requirement, $X$.  In other
+words it may be practical to estimate that each model task requirement is
+within $P\%$ of the actual task requirement.  Although that means $\hat{X}$
+may under- or overestimate $X$ by as much as $P\%$, in order to prevent
+underestimating we can adjust $\hat{X}$ as in Eq. \ref{eq:pbias}, hereafter
+referred to as the proportionate bias strategy.
 
 \begin{equation}
-\label{eq:cpueff}
-e_c = \begin{cases}
-	1, ~~~~~~~~\ell_c < 4 \\
-	(4/\ell_c), ~~\ell_c \ge 4
-\end{cases}
+\hat{X^b} \xleftarrow{p} \hat{X} / (1 - P\%)
+\label{eq:pbias}
 \end{equation}
 
+Although the proportionate bias strategy can effectively eliminate
+underestimated model task requirements with a judiciously chosen $P\%$
+which may require less knowledge about the nature of the error than choosing
+a proper magnitude for the constant bias strategy value, $C$, this relaxed
+requirement comes at a price.  Specifically, where the constant bias
+strategy increases the maximum overestimate of actual task requirement, $X$
+inherent in $\hat{X}$ by $C$, the proportionate bias strategy `stretches'
+the distribution of $\hat{X^b}$ and yields a much larger range of
+overestimates.  This is illustrated in Figure \ref{fig:cpbias} where the
+distribution of an example model value is adjusted according to the constant
+and proportionate bias strategies.  For both adjustments, an ideal value of
+$C$ and $P$ are shown, though practically an ideal value wouldn't be known
+and have to be estimated itself.
+
+\begin{figure}
+	\begin{center}
+		\includegraphics[width=0.5\textwidth]{figures/BiasVisualization_Constant.pdf}
+		\includegraphics[width=0.5\textwidth]{figures/BiasVisualization_Proportionate.pdf}
+	\end{center}
+	\caption{Illustration of probabilities for a model task requirement
+		with bound error as a percentage, $P$, of the actual task
+		requirement, $X$, and the effect of constant and proportionate
+		bias strategies transforming the distribution into
+		one that never underestimates the actual term, $X$, given an
+		ideal value for $C$ and $P$.  Distribution is assumed to be
+		zero-mean and triangular.}
+	\label{fig:cpbias}
+\end{figure}
+
+In order to achieve a less `stretched' distribution for the biased model task
+requirement than the proportionate bias strategy while still maintaining the
+need only for an estimated maximum percentage, not magnitude, of error, the
+third proposed strategy, known as the simple bias strategy, is given in Eq.
+\ref{eq:sbias}.  It fails to eliminate the possibility of underestimating
+though it does reduce its propability substantially, but also prevents wildly
+overestimating task requirements by decreasing the amount of `stretch' in the
+biased term's distribution.  Figure \ref{fig:sbias} illustrates the effect of
+the simple bias strategy on the distribution of the biased term.
+
 \begin{equation}
-\label{eq:memeff}
-e_m = \frac{10}{10 + \frac{1}{(1/\ell_m) - 1}}
+\hat{X^b} \xleftarrow{s} \hat{X} (1 + P\%)
+\label{eq:sbias}
 \end{equation}
 
-For all numeric results for
-performance the value presented is an averaged value across ten simulations
-where the workflows and tasks were the same but a unique random error term,
-$x$, was used for each model task's required CPU cycles.
+\begin{figure}
+	\begin{center}
+		\includegraphics[width=0.5\textwidth]{figures/BiasVisualization_Simple.pdf}
+	\end{center}
+	\caption{Illustration of probabilities for a model task requirement
+		with bound error as a percentage, $P$, of the actual task
+		requirement, $X$, and the effect of the simple bias strategy
+		transforming the distribution, given an ideal value for $P$.
+		Distribution is assumed to be zero-mean and triangular.}
+	\label{fig:cpbias}
+\end{figure}
+
+\section{Results}
+\label{sec:Results}
+
+All results were collected using simulations performed using simulator software
+developed for previous research \cite{costmin} and \cite{pdpta18} and made
+publically available as open source \cite{soasim}.  Workflows and task
+requirements are the same as those in \cite{pdpta18} as are simulated error
+amounts which ranged from $0.1\%$ up to $90\%$ taken from a uniform
+distribution.  For all numeric results for performance the value presented is
+an averaged value across ten simulations where the workflows and tasks were
+identical but a error term applied to model tasks' requirements were unique.
 
@@
 		bars) and with 0.1\% error applied to the model of the workflow
-		requirements (line graphs).  In this scenario, task completion event
-		feedback was \textbf{not} employed to correct the model platform.}
-	\label{fig:noloss-lowerror-nofeedback}
+		requirements (line graphs).  Complete feedback of task completion from
+		the actual platform was used, but model platform was, due to
+		underestimated task requirements, allowed to model tasks as completing
+		and subsequenting scheduling algorithms allowed to schedule additional
+		tasks to the machine.}
+	\label{fig:noloss-nobias-lowerror}
 \end{figure*}
 
-\section{Results}
-\label{sec:Results}
+Figure \ref{fig:noloss-nobias-lowerror} shows the performance of the four
+scheduling algorithms and the significant performance impact that the smallest
+amount of error tested has even when complete feedback is available from the
+actual platform but the model platform is still allowed to model tasks as
+completing early due to underestimates of task requirements. In this figure
+as with prior research, performance is depicted visually as a histogram of the
+number of workflows completed in intervals based on their normalized tardiness
+(the time difference between the completion and the target deadline normalized
+by amount of time available to execute the workflow, i.e., the difference of
+deadline and arrival time of the workflow). In this representation a normalized
+tardiness of 0 represents a workflow that completed exactly at its deadline,
+negative values represent workflows completed before their deadline, and
+positive values those completed late.
 
-Figure \ref{fig:noloss-lowerror-nofeedback} shows the performance of scheduling
-algorithms and the significant performance impact that even a small amount of
-error has.  In this figure as with prior research, performance is depicted
-visually as a histogram of the number of workflows completed in intervals based
-on their normalized tardiness (the time difference between the completion and
-the target deadline normalized by on-time completion time of the workflow).
-In this representation a normalized tardiness of 0 represents a workflow that
-completed exactly at its deadline, negative values represent workflows completed
-before their deadline, and positive values those completed late.
-
-The histogram bars of Figure \ref{fig:noloss-lowerror-nofeedback} represent the
+The histogram bars of Figure \ref{fig:noloss-nobias-lowerror} represent the
 performance of scheduling algorithms under the ideal circumstance of no error
@@
 algorithm performs relatively poorly with workflows completing far later than
-their deadline because it is oblivious to deadlines and therefore often will
-put off scheduling tasks of a recently-arrived workflow with a `tight' deadline
-by prioritizing a less-recently arrived workflow despite its deadline being
-further into the future and possibly more relaxed.
+their deadline because the algorithm doesn't use deadline information in making
+its scheduling decisions.
 
-The lines graphed in Figure \ref{fig:noloss-lowerror-nofeedback} represent the
+The lines graphed in Figure \ref{fig:noloss-nobias-lowerror} represent the
 same algorithms' histogram of workflow completion in the presence of 0.1\% error
-in the model platform.  As depicted, one algorithm (CMSA algorithm optimizing
-the cost based on a Sigmoid cost function) maintains roughly the same
-performance in the presence of this small model error, as without it.  All three
-other algorithms exhibit a dramatic loss in performance, i.e., a shift of many
-workflows completing ahead of or shortly after their deadline to completing
-many times over later than their deadline.  In this scenario, completion events
-were \textbf{not} employed to correct the model platform.
+in the model platform.  Due even to this small amount of error, the problem of
+underestimating task requirements and overallocating resources, and the nature
+of this issue compounding results in all four scheduling algorithms exhibiting
+substantially worse performance.  This is illustrated by the reduction to less
+than half as many workflow completed before their deadlines (normalized
+tardinesses less than 0) compared to the no-error case.  It is also
+demonstrated by the large increase of number of workflows completed with a
+normalized tardiness of 10 or higher compared to the no-error case.
 
-\begin{table}
-       \begin{center}
-       \begin{tabular}{lllll}
-\textbf{Error, }$X$ & \textbf{CMSA}	& \textbf{CMSA}				& \textbf{FCFS}				& \textbf{PLLF} \\
-		& \textbf{(Quad)}			& \textbf{(Sig)}			&							& \\
-0.0		& \cellcolor{red! 6}16.54	& \cellcolor{green!9}1.77	& \cellcolor{red!28}38.49	& \cellcolor{red!28}38.72 \\
-0.001	& \cellcolor{red!20}30.52	& \cellcolor{green!9}1.92	& \cellcolor{red!51}61.39	& \cellcolor{red!40}50.96 \\
-0.005	& \cellcolor{red!24}34.75	& \cellcolor{green!9}1.84	& \cellcolor{red!49}59.48	& \cellcolor{red!42}52.39 \\
-0.01	& \cellcolor{red!20}30.86	& \cellcolor{green!7}2.99	& \cellcolor{red!50}60.35	& \cellcolor{red!39}49.39 \\
-0.05	& \cellcolor{red!18}28.87	& \cellcolor{green!1}8.99	& \cellcolor{red!53}63.60	& \cellcolor{red!39}49.54 \\
-0.1		& \cellcolor{red!22}32.11	& \cellcolor{red! 5}15.60	& \cellcolor{red!50}60.77	& \cellcolor{red!42}52.65 \\
-0.5		& \cellcolor{red!24}34.34	& \cellcolor{red!14}24.96	& \cellcolor{red!42}52.85	& \cellcolor{red!45}55.68 \\
-0.9		& \cellcolor{red!22}32.93	& \cellcolor{red!16}26.12	& \cellcolor{red!44}54.36	& \cellcolor{red!48}58.64 \\
-       \end{tabular}
-       \caption{Percent of workflows late for four scheduling algorithms
-			across various amounts of error in the model platform.  Completion
-			events were \textbf{not} employed to correct the model platform.}
-       \label{tab:perclate}
-       \end{center}
-\end{table}
-
-Table \ref{tab:perclate} lists the value of percent of all workflows completed
-late (after their deadline) as a single performance metric for the scheduling
-algorithms across various amounts of the error term, $X$.  This metric (percent
-late workflows) is useful in comparing the impact of increasing error on the
-performance of each scheduling algorithm.  Like Figure
-\ref{fig:noloss-lowerror-nofeedback}, it illustrates how CMSA (with sigmoid cost
-function) is robust to small error, whereas the other algorithms are not.  It
-also shows that while the performance of CMSA (Sig) degrades as error increases,
-the other three algorithms maintain nearly a constant level of even poorer
-performance with any amount of error.  These results show how some algorithms
-(CMSA with Sigmoid cost function) can be relatively robust (at least with
-respect to this performance metric) for small amounts of error but how all
-algorithms eventually perform poorly when using a model platform that fails to
-reasonably represent the actual system.
-
-The model task requirement with respect to the amount of CPU cycles each task
-requires has a compounding effect when the model system declares, erroneously,
-that a task has completed (ahead of the actual system) and thus the scheduler
-determine to begin execution of an additional task that increases the system
-resource load in the actual system and slows the progression toward completion
-even further.  Intuitively, this compounding error is most likely the reason
-for such a dramatic decrease in overall scheduler performance for the three
-affected algorithms of Figure \ref{fig:noloss-lowerror-nofeedback}.
-
-\begin{figure*}
-	\begin{center}
-		\includegraphics[width=0.9\textwidth,height=3in]{figures/Histogram_All_NoLoss_NoBias_HighErrorWithoutModelFinishEvents.pdf}
-	\end{center}
-	\caption{Histogram of workflows by normalized tardiness comparing relative
-		performance of scheduling algorithms with no error (vertical bars) and
-		with 90\% error applied to the model of the workflow requirements
-		(line graphs).  In this scenario, task completion event feedback
-		\textbf{was} employed to correct the model platform.}
-	\label{fig:noloss-higherror-nomodel}
-\end{figure*}
-
-The strategy proposed in this paper is to incorporate feedback from the actual
-platform for task completions as an event-based trigger for updating the
-model platform and allowing the scheduler to schedule new tasks.  Figure
-\ref{fig:noloss-higherror-nomodel} depicts results of the performance of
-scheduling algorithms comparable with Figure
-\ref{fig:noloss-lowerror-nofeedback} except that the error introduced in the
-model is much higher (90\%, instead of 0.1\%) and the model platform uses task
-completion events from the actual platform (instead of relying on the model
-platform estimates of task completions).  Given that the line graphs match
-much more closely to the vertical bars than in Figure
-\ref{fig:noloss-lowerror-nofeedback}, this illustrates how even for large
-model error the incorporation of actual platform task completion feedback
-increases the robustness of all four scheduling algorithms.  The CMSA (Sig)
-algorithm which was robust for small amounts of error, as well as the other
-three algorithms which were not robust even for the smallest amount of error
-studied (0.1\%) all achieve nearly the same level of performance (i.e. shape
-of histogram) as with having a perfect, no-error model.
+Therefore, with any level of partial feedback available it is unexpected that
+any of these scheduling algorithms would perform better than the case of
+complete feedback being available but still allowing modeling of early task
+completions due to underestimated task requirements.  However, the use of
+model task requirement biasing showed promising results at restoring
+performance of the algorithms by eliminating or reducing the likelihood of
+the underestimating problem.
 
@@
 \label{sec:Summary}
-
-In this paper we introduced a framework for understanding and evaluating
-scheduling algorthms' performance and robustness with
-respect to error in tasks' resource requirements.  This framework
-incorporates a model of the actual system in which errors and uncertainties can
-be represented.  Through simulation studies we examined the performance of four
-scheduling algorithms and the impact of error in the model system upon their
-performance.  While the CMSA algorithm (using a sigmoid cost function) had some
-degree of robustness, i.e. it was able to achieve similar performance in the
-presence of very small error, all algorithms exhibited poor performance with
-even moderate amounts of error present in one dimension of the model workflows
-requirements (CPU cycles required for the tasks).
-
-We also introduced and simulated the notion of incorporating feedback from
-the actual system back into the model system.  Through simulation studies we
-showed how all algorithms can benefit from feedback of task completion events
-and thus become relatively robust to even substantial error in the model
-system.
-
-In the present paper, we assumed that tasks' completion events are detected
-and fed back in order to `correct' the model platform.  Under this
-assumption, the model completely relies on actual completion events being
-fed back.  Future work will consider the possibility in which partial feedback
-(of some) completion events are available and fed back to the model.  This
-`partial feedback' assumption may be more practical than the complete feedback
-used in this paper in situations where there would be significant overhead
-instrumenting the actual system so as to feed back each and every completion
-event.  In such cases, taking small samplings of completion events from the
-actual system would be more practical. Finally, future work will also
-investigate the effect of non-uniform error and/or error distributions without
-an expected value of $0$.
 

### 2019-04-26 paper.tex
Complete Result and Summary sections.

@@
 
-\title{\bf A Model-Based Scheduling Framework for Enhancing Robustness}
+\title{\bf Enhancing Scheduling Robustness with Feedback and Biasing}
 
@@
 \end{figure}
+
+Four scheduling algorithms were studied in this and previous work.  The first
+is First-Come, First-Served (FCFS) which prioritizes scheduling tasks from
+workflows which arrived earlier over tasks from workflows that arrived later.
+The second is Proportional-Least Laxity First which projects a finish time
+of a task's workflow based on the rate of completion of its tasks in the past
+and then prioritizes tasks from workflows projected to be completed most tardy
+proportional to the overall size of the workflow.  The final two are variants
+of the Cost-Minimization Scheduling Algorithm (CMSA) \cite{costmin} which
+projects a finish time of a task's workflow (as with PLLF) and uses a cost
+function to assign as cost to the projected tardiness.  CMSA is used with two
+cost functions: a quadratic cost function and sigmoid cost function.
 
@@
 		Distribution is assumed to be zero-mean and triangular.}
-	\label{fig:cpbias}
+	\label{fig:sbias}
 \end{figure}
@@
 requirements are the same as those in \cite{pdpta18} as are simulated error
-amounts which ranged from $0.1\%$ up to $90\%$ taken from a uniform
+amounts which ranged from $0.1\%$ up to $50\%$ taken from a uniform
 distribution.  For all numeric results for performance the value presented is
@@
 	\begin{center}
-		\includegraphics[width=0.9\textwidth,height=3in]{figures/Histogram_All_NoLoss_NoBias_LowError.pdf}
+		\includegraphics[width=0.9\textwidth,height=3in]{figures/Histogram_All_NoLoss_NoBias_LowAllError.pdf}
 	\end{center}
@@
 
+Figure \ref{fig:nofeedback-cbias-higherror} depicts the effect of the constant
+bias strategy in the present of the highest ($50\%$) error tested with no
+feedback (the lines of the graph) against the no-error ideal case (the bars
+of the graph).  Key results are that for constant bias strategy is of no
+help to the FCFS algorithm which completes the majority of workflows with a
+normalized tardiness of $10$ or above.  For the PLLF algorithm, nearly as
+many workflows are no longer completed on time as for FCFS but the maximum
+normalized tardiness of workflows remains bounded at about $4$.  Both
+variants of CMSA seem to similarly complete fewer overall workflows on time
+through for the Quadratic cost function variant those workflows seem to be
+completed mostly at $0.5$ normalized tardiness and below while for the
+Sigmoid cost function variant they are spread from normalized tardinesses
+under $0.25$ up to $10+$. Although not depicted, for smaller bounded errors,
+the constant bias strategy does expectedly better, achieving results nearly
+as good as the no-error ideal case for errors up to about $5\%$.
+
+\begin{figure*}
+	\begin{center}
+		\includegraphics[width=0.9\textwidth,height=3in]{figures/Histogram_All_CompleteHighAllUniformError_WithCBias.pdf}
+	\end{center}
+	\caption{Histogram of workflows by normalized tardiness comparing
+		relative performance of scheduling algorithms in ideal case with no
+		error (vertical bars) and with 50\% error applied to the model of the
+		workflow requirements (line graphs) given no feedback of task
+		completion times and using the constant bias strategy with ideal
+		constant to prevent underestimating task requirements in even the
+		worst instance of error.}
+	\label{fig:nofeedback-cbias-higherror}
+\end{figure*}
+
+Neither the proportionate nor simple bias strategies achieve acceptible
+results with errors as high as $50\%$.  In Figures
+\ref{fig:nofeedback-pbias-mederror} and \ref{fig:nofeedback-sbias-mederror}
+the effect of proportionate and simple bias strategies are shown, respectively,
+in the case of $5\%$ error with no feedback and ideal bias value $P=5\%$.
+In the case of Figure \ref{fig:nofeedback-pbias-mederror} and proportionate
+bias strategy all four scheduling algorithms complete about one third fewer
+workflows at a normalized tardiness of $-0.25$ and below although most of those
+workflows are instead completed at normalized tardiness up to $0$, so they are
+still completed before their deadline.  CMSA with both cost functions completes
+a few more workflows mildly late (normalized tardiness $0.25$ and below), PLLF
+completes more workflows at normalized tardinesses up to $1$, and FCFS a few
+more at $4+$.  Overall, the proportionate bias strategy fairly effectively
+makes all scheduling algorithms robust to errors up to $5\%$ even without any
+actual platform feedback available.
+
+The simple bias strategy achieves an even better result than the proportionate
+bias strategy for the $5\%$ bounded error case, showing fewer workflows
+shifting from being completed early to completed late.  In fact, the CMSA with
+Sigmoid cost function appears to achieve nearly identical results despite no
+feedback and up to $5\%$ error when using the simple bias strategy.  It
+therefore appears that the small chance for simple bias strategy to still
+underestimate task requirements is a better tradeoff than the exagerrated
+overestimates produced by the proportionate bias strategy.
+
+\begin{figure*}
+	\begin{center}
+		\includegraphics[width=0.9\textwidth,height=3in]{figures/Histogram_All_CompleteMediumAllUniformError_WithRBias.pdf}
+	\end{center}
+	\caption{Histogram of workflows by normalized tardiness comparing
+		relative performance of scheduling algorithms in ideal case with no
+		error (vertical bars) and with 5\% error applied to the model of the
+		workflow requirements (line graphs) given no feedback of task
+		completion times and using the proportionate bias strategy with ideal
+		$P=5\%$ to prevent underestimating task requirements in even the
+		worst instance of error.}
+	\label{fig:nofeedback-pbias-mederror}
+\end{figure*}
+
+\begin{figure*}
+	\begin{center}
+		\includegraphics[width=0.9\textwidth,height=3in]{figures/Histogram_All_CompleteMediumAllUniformError_WithBias.pdf}
+	\end{center}
+	\caption{Histogram of workflows by normalized tardiness comparing
+		relative performance of scheduling algorithms in ideal case with no
+		error (vertical bars) and with 5\% error applied to the model of the
+		workflow requirements (line graphs) given no feedback of task
+		completion times and using the simple bias strategy with ideal
+		$P=5\%$ to nearly prevent underestimating task requirements in even the
+		worst instance of error.}
+	\label{fig:nofeedback-sbias-mederror}
+\end{figure*}
+
 \section{Summary and Future Work}
 \label{sec:Summary}
+
+In this paper we presented the case for why complete and reliable feedback
+of scheduled task completions from an actual platform to the model used for
+scheduling decision-making was found to be necessary to achieve robust
+performance of scheduling algorithms in previous work \cite{pdpta18}.
+Furthermore we have demonstrated the use of partial feedback as insufficient
+at achieving that robustness, but have proposed the use of biasing the model
+parameters to prevent or reduce the likelihood of the model underestimating
+task requirements thereby modeling tasks as completing earlier than their
+actual completion.
+
+Three biasing strategies were proposed, each with different assumptions of
+what knowledge is available about the error inherent in the model and
+different tradeoffs of balancing the amout of overestimation vs. likelihood
+of underestimation of task requirements.  Through simulated case studies we
+demonstrated that each biasing strategy is useful for achieving robustness
+of scheduling algorithm performance at different amount of model error.
+
+Future work that remains includes analysis of whether the combination of
+partial feedback with any of the biasing strategies can achieve greater
+robustness.  Additionally, other biasing strategies or alternatives to
+biasing will be explored to increase robustness or address cases where
+the amount of error in the model is unknown.  Finally, the use of more
+sophisticated approaches such as machine learning may be applied to either
+supplement or replace feedback information from the actual platform.
 

### 2019-04-27 paper.tex
Incorporate Dr Antonio's comments in wordsmithing and make all figures have the same y axis range.

@@
 
-\title{\bf Enhancing Scheduling Robustness with Feedback and Biasing}
+\title{\bf Enhancing Scheduling Robustness with Task Completion Feedback and
+Resource Requirement Biasing}
 
@@
 \begin{abstract}
-In previous work the performance of scheduling algorithms for dynamic
-scheduling of tasks in a distributed system were evaluated for their
-robustness to error in the model of tasks' information.  There it was
-found that incorporating task completion timings from the actual distributed
+Performance and robustness of dynamic scheduling algorithms are evaluated in
+the presence of errors in the tasks' resource requirements.  Previous work
+found that incorporating task completion events from the actual distributed
 system into the algorithms' model of the system was crucial for achieving
-robustness.  In this paper, various degrees of feedback, rather than simply
+robustness.  In the present, various degrees of feedback, rather than simply
 all-or-none, are evaluated using the same simulated studies as in previous
@@
 
-Such algorithms for dynamic scheduling may be based on heuristics for selecting
-which tasks to prioritize execution of and determining when to begin their
-execution and on which machine. Other algorithms may actively attempt to
-optimize scheduling decisions with respect to a desired outcome based on a
-user-defined objective.  Both types of algorithms are generally measured
-and compared to one another against such objectives such as minimizing makespan
-(time required for completed execution of all tasks) \cite{stochastic}, or, as
-in this paper, the degree to which all tasks of a DAG are completed by a
-DAG-associated deadline.
+Another dimension in the taxonomy of scheduling algorithms deals with whether
+tasks are executed `one at a time' on the machine to which they are assigned.
+In the present work, multiple tasks may be executed concurrently on a single
+machine.
+
+Algorithms for dynamic scheduling may be based on heuristics for selecting
+which tasks to prioritize and determining when to begin their execution and on
+which machine. Other algorithms attempt to optimize scheduling decisions with
+respect to a desired outcome based on a user-defined objective.  Both types of
+algorithms are generally measured and compared to one another against such
+objectives such as minimizing makespan (time required for completed execution
+of all tasks) \cite{stochastic}, or, as in this paper, the degree to which all
+tasks of a DAG are completed by a DAG-associated deadline.
 
@@
 for example, how well the same objective is achieved when information provided
-to the scheduling algorithm contains errors such as inaccuracies in the
-amount of resource requirements of the tasks.  In previous work \cite{pdpta18}
-four dynamic scheduling algorithms' robustness to error with respect to
-performance against an objective of completing DAGs before their deadline was
-presented, showing how some algorithms were not robust to even the smallest
-amount of simulated error.  Additionally, the use of task completion time
-feedback from the actual distributed system back into the modeled system used
-by the scheduling algorithms was found to substantially improve robustness of
-all four scheduling algorithms to even large amounts of simulated error.
+to the scheduling algorithm contains errors such as inaccuracies in resource
+requirements of the tasks.  In previous work \cite{pdpta18} four dynamic
+scheduling algorithms' robustness to error with respect to performance against
+an objective of completing DAGs before their deadline was presented, showing
+how some algorithms were not robust to even the smallest amount of error. The
+use of task completion event feedback from the actual distributed system back
+into the modeled system used by the scheduling algorithms was found to
+substantially improve robustness of all four scheduling algorithms even with
+large amounts of error.
 
@@
 \ref{sec:Framework} describes the problem domain and the simulation software's
-use of modeling the distributed system where errors in task requirements may
-be inherent.  Section \ref{sec:Biasing} presents an approach to counteracting
-model error to prevent scheduling algorithms from over-committing system
-resources to executing too many tasks concurrently. Section \ref{sec:Results}
-presents results of simulated case studies within that software simulator.
+use of modeling the distributed system in which errors in task requirements may
+be present.  Section \ref{sec:Biasing} presents a requirements biasing approach
+to counteracting model error to prevent scheduling algorithms from
+over-committing system resources to executing too many tasks concurrently.
+Section \ref{sec:Results} presents results of simulated case studies.
 Finally, Section \ref{sec:Summary} summarizes the findings from these
@@
 
-\section{Problem Domain and Simulation Environment}
+\section{Problem Domain and \\
+Simulation Environment}
 \label{sec:Framework}
@@
 workflows) was introduced.  Four scheduling algorithms were tested in a
-simulation environment \cite{soasim} given the same 24-hour simulated period
+simulation environment \cite{soasim} given a 24-hour simulated period
 of arriving workflows ranging in size from 5 tasks up to 800.  Each workflow
-had a known, predetermined deadline and scheduling algorithms were evaluated
-based both on the number of workflows completed before their deadline and the
-distribution of workflow counts completed at various normalized proportions
-past their deadline (e.g., workflows up to 100\% late relative to the amount
-of time between their arrival and deadline).
+has a known, predetermined deadline and scheduling algorithms were evaluated
+in \cite{pdpta18} based both on the number of workflows completed before their
+deadline and the distribution of workflow counts completed at various
+normalized proportions past their deadline (e.g., workflows up to 100\% late
+relative to the amount of time between their arrival and deadline).
 
-Scheduling algorithms are used to determine from a given queue of tasks
+Scheduling algorithms are used to determine \textemdash from a given queue of tasks
 ready to begin executing (i.e. tasks of arrived workflows that have no
-precedence constraints or whose precedent tasks have all completed) both
-when the task should begin executing and on which machine of the platform.
-Unlike some scheduling research, tasks are permitted to executing concurrently
-with other tasks on the same machine which increases machines' overall load
-on resources such as CPU and memory and thereby slows the rate of work on each
-executing task.  Original work in \cite{pdpta09} details this non-linear
-degradation of rate of work (efficiency) due to concurrent task execution.
+precedence constraints or whose precedent tasks have all completed)
+\textemdash both when the task should begin executing and on which machine of
+the platform. Unlike some scheduling research, tasks are permitted to executed
+concurrently with other tasks on the same machine, which increases machines'
+overall load on resources such as CPU and memory and thereby slows the rate of
+work on each executing task.  Original work in \cite{pdpta09} details this
+non-linear degradation of rate of work (efficiency) due to concurrent task
+execution.
 
@@
 flow of information within the model-based approach to executing and evaluating
-scheduling algorithms.  Whereas the modeled tasks' requirements (CPU load,
+scheduling algorithms.  The modeled tasks' requirements (CPU load,
 required number of CPU cycles, and memory load) may contain errors relative to
-the true values of those tasks, the model platform may diverge from the
-actual platform in terms of which tasks are completed and which are still
-executing.
+the true values of those tasks; these errors then cause the model platform to
+diverge from the actual platform in terms of which tasks are completed and
+which are still executing.
 
@@
 is First-Come, First-Served (FCFS) which prioritizes scheduling tasks from
-workflows which arrived earlier over tasks from workflows that arrived later.
+workflows that arrived earlier over tasks from workflows that arrived later.
 The second is Proportional-Least Laxity First which projects a finish time
-of a task's workflow based on the rate of completion of its tasks in the past
-and then prioritizes tasks from workflows projected to be completed most tardy
-proportional to the overall size of the workflow.  The final two are variants
-of the Cost-Minimization Scheduling Algorithm (CMSA) \cite{costmin} which
-projects a finish time of a task's workflow (as with PLLF) and uses a cost
-function to assign as cost to the projected tardiness.  CMSA is used with two
-cost functions: a quadratic cost function and sigmoid cost function.
+of a task's overarching workflow based on the rate of completion of its tasks
+in the past and then prioritizes tasks from workflows projected to be
+completed most tardy proportional to the overall size of the workflow. The
+final two algorithms are variants of the Cost-Minimization Scheduling Algorithm
+(CMSA) \cite{costmin}, which projects a finish time of a task's workflow (as
+with PLLF) and uses a cost function to assign a cost to the projected
+tardiness. CMSA is used with two cost functions: a quadratic cost function and
+sigmoid cost function.
 
 All four studied scheduling algorithms were shown to be sensitive to
-even small amounts of error in modeled tasks.  Each scheduling algorithm
-exhibited a decreased percent of workflow completed ahead of their deadline
-with the smallest amount of error studied.  For three of the scheduling
-algorithms the decrease was substantial, but relatively equal, regardless of
-the amount of error.  For the fourth scheduling algorithm, the decrease was
-less severe overall and was propotionate to the amount of error.  The
-fourth algorithm was thus declared to be somewhat robust to small amounts of
-error (less than 0.5\%) but ultimately, like all three others, was not
+even small amounts of error in modeled tasks \cite{pdpta18}.  Each scheduling
+algorithm exhibited a decreased percent of workflow completed ahead of their
+deadline with the smallest amount of error studied.  For three of the
+scheduling algorithms the decrease was substantial, but relatively equal,
+regardless of the amount of error.  For the fourth scheduling algorithm, the
+decrease was less severe overall and was propotionate to the amount of error.
+The fourth algorithm was thus declared to be somewhat robust to small amounts
+of error (less than 0.5\%) but ultimately, like all three others, was not
 robust for errors of 1\% or greater.
@@
 The main result of \cite{pdpta18} showed that incorporating feedback of
-task completions from the actual platform to the model platform thereby
+task completions from the actual platform to the model platform (thereby
 preventing the model platform from modeling a task completing before the
-actual task completed dramatically increased robustness of all scheduling
-algorithms for even errors up to 90\% (the highest amount studied).  Figure
-\ref{fig:underestimating} illustrates why the model platform underestimating
-the requirements of a task and thereby modeling it as completed ahead of the
-actual task can be so detrimental.
+actual task completed) dramatically increased robustness of all scheduling
+algorithms, even for errors up to 90\% (the highest amount studied) in the
+modeled tasks' requirement for amount of work in CPU cycles.  Figure
+\ref{fig:underestimating} illustrates why the model platform's underestimation
+of the requirements of a task (and thereby modeling it as completed ahead of
+the actual task) can be so detrimental.
 
@@
 $t_1$ and $t_2$ to have actual completion times later than the modeled
-completion times because of the unintentionally-overallocated resources of
+completion times because of the unintentional over allocation of resources of
 the machine executing the tasks.  By extension, if another task, say $t_3$,
 were to be scheduled to begin after $t_2$ finishes this problem could compound
-because $t_2$'s actual completion would delayed by concurrent execution with
-$t_1$ and further delayed by concurrent execution with $t_3$.
+because $t_2$'s actual completion would be further delayed by the additional
+concurrent execution with $t_3$.
 
-The previous example illustrates why allowing the model to platform to
+The previous example illustrates why allowing the model platform to
 inform scheduling algorithms when tasks are complete and machines are
-idle (or less loaded) in the presense of error which may underestimate tasks'
-true requirements can be so detrimental.  With feedback of every task's
-completion from the actual platform the modeled completion times of tasks
+idle (or less loaded) in the presense of error (which may underestimate tasks'
+true requirements) can be so detrimental.  With feedback of every task's
+completion from the actual platform, the modeled completion times of tasks
 may be safely ignored.  However, complete feedback of all tasks' completion
@@
 of tasks' completion times may be sufficient to achieve some level of
-robustness to model error.  In addition, based specifically on the
-knowledge of the underestimating problem illustrated prior, in Section
-\ref{sec:Biasing} that follows a specific approach to counteracting
-that problem by biasing model task requirements is proposed.  Results of
-both partial feedback and biasing are presented in Section \ref{sec:Results}.
+robustness to model error.  In addition, based specifically on the knowledge
+of the underestimating problem illustrated prior, Section \ref{sec:Biasing}
+proposes a specific approach to counteracting that problem by biasing model
+task requirements.  Results of both partial feedback and biasing are presented
+in Section \ref{sec:Results}.
 
@@
 unintentionally-concurrent with other tasks, delaying their completion.
-However, if the model is known to have error which may underestimate
-task requirements, then the model task requirements could simply be
-biased by increasing its value in order to reduce (or ideally, eliminate)
-the probability that it underestimates the actual task requirements.
-In this section three proposed strategies for biasing model task
-requirements are proposed.
+However, if the model is known to have error which may underestimate task
+requirements, then the model task requirements could simply be biased by
+increasing its assumed (provided) value in order to reduce (or ideally,
+eliminate) the probability that it underestimates the actual task requirements.
+In this section three proposed strategies for biasing model task requirements
+are proposed.
 
-The simplest form of biasing would be to add a constant value to each
-task requirement.  If the maximum magnitude of error for which a model
+The simplest form of biasing is to add a constant value to each task
+requirement.  If the maximum magnitude of error for which a model
 task requirement may underestimate the actual task requirement is known,
 then that value would be the ideal bias constant value because it would
-eliminate the model from ever underestimating task requirements but
-bound the worst overestimate to the smallest amount possible for such a
-constant value biasing strategy.  Practically, the maximum error magnitude
-is unlikely to be known, though because it is the most ideal circumstance
-for biasing it is included here and in simulated results of Section
-\ref{sec:Results}.  The equation for a simple constant bias value, $C$,
-addition to each model task requirement, $\hat{X}$, to yield a biased
-model task requirement, $\hat{X^b}$, is given in Eq.
-\ref{eq:cbias}.
+eliminate the model from ever underestimating task requirements while
+minimizing the amount of overestimation. Practically, the maximum error
+magnitude is unlikely to be known. However, because it is the most ideal
+circumstance for biasing it is included here and in simulated results of
+Section \ref{sec:Results}. The equation for a simple constant bias value, $C$,
+addition to each model task requirement, $\hat{X}$, to yield a biased model
+task requirement, $\hat{X^b}$, is given in Eq. \ref{eq:cbias}.
 
@@
 
-A more practical approach biasing model task requirements is to assume a bound,
-not on the magnitude of error, but on the fraction or percentage of error.  It
-may be possible, for example, through analysis of past executions of tasks and
-workflows, to estimate the maximum percentage of error for each model task
-requirement, $\hat{X}$, relative to the actual task requirement, $X$.  In other
-words it may be practical to estimate that each model task requirement is
-within $P\%$ of the actual task requirement.  Although that means $\hat{X}$
+A more realistic approach to biasing model task requirements is to assume a
+bound, not on the magnitude of error, but on the fraction or percentage of
+error. It may be possible, for example, through analysis of past executions of
+tasks and workflows, to estimate the maximum percentage of error for each model
+task requirement, $\hat{X}$, relative to the actual task requirement, $X$. In
+other words it may be practical to estimate that each model task requirement is
+within $P\%$ of the actual task requirement.  Although that implies $\hat{X}$
 may under- or overestimate $X$ by as much as $P\%$, in order to prevent
@@
 requirement comes at a price. Specifically, where the constant bias
-strategy increases the maximum overestimate of actual task requirement, $X$
-inherent in $\hat{X}$ by $C$, the proportionate bias strategy `stretches'
-the distribution of $\hat{X^b}$ and yields a much larger range of
-overestimates.  This is illustrated in Figure \ref{fig:cpbias} where the
-distribution of an example model value is adjusted according to the constant
-and proportionate bias strategies.  For both adjustments, an ideal value of
-$C$ and $P$ are shown, though practically an ideal value wouldn't be known
-and have to be estimated itself.
+strategy shifts the actual task requirement by $C$, the proportionate bias
+strategy `stretches' the distribution of $\hat{X^b}$ and yields a much larger
+range of overestimates. This is illustrated in Figure \ref{fig:cpbias} where
+the distribution of an example model value is adjusted according to the
+constant and proportionate bias strategies.  For both adjustments, an ideal
+value of $C$ and $P$ are shown, though practically an ideal value wouldn't be
+known and have to be estimated itself.
 
@@
 		one that never underestimates the actual term, $X$, given an
-		ideal value for $C$ and $P$.  Distribution is assumed to be
-		zero-mean and triangular.}
+		ideal value for $C$ and using the exact value of $P$ (the bounded
+		error) in the proportionate bias strategy's Eq. \ref{eq:pbias}.
+		Distribution is assumed to be zero-mean and triangular.}
 	\label{fig:cpbias}
@@
 third proposed strategy, known as the simple bias strategy, is given in Eq.
-\ref{eq:sbias}.  It fails to eliminate the possibility of underestimating
-though it does reduce its propability substantially, but also prevents wildly
-overestimating task requirements by decreasing the amount of `stretch' in the
-biased term's distribution.  Figure \ref{fig:sbias} illustrates the effect of
-the simple bias strategy on the distribution of the biased term.
+\ref{eq:sbias}. This third strategy fails to eliminate the possibility of
+underestimating though it does reduce its propability substantially, but also
+prevents wildly overestimating task requirements by decreasing the amount of
+`stretch' in the biased term's distribution.  Figure \ref{fig:sbias}
+illustrates the effect of the simple bias strategy on the distribution of the
+biased term.
 
@@
 
-In this paper we presented the case for why complete and reliable feedback
-of scheduled task completions from an actual platform to the model used for
-scheduling decision-making was found to be necessary to achieve robust
-performance of scheduling algorithms in previous work \cite{pdpta18}.
-Furthermore we have demonstrated the use of partial feedback as insufficient
-at achieving that robustness, but have proposed the use of biasing the model
-parameters to prevent or reduce the likelihood of the model underestimating
-task requirements thereby modeling tasks as completing earlier than their
-actual completion.
-
-Three biasing strategies were proposed, each with different assumptions of
-what knowledge is available about the error inherent in the model and
-different tradeoffs of balancing the amout of overestimation vs. likelihood
-of underestimation of task requirements.  Through simulated case studies we
-demonstrated that each biasing strategy is useful for achieving robustness
-of scheduling algorithm performance at different amount of model error.
+The case for why complete and reliable feedback of scheduled task completions
+from an actual platform to the model used for scheduling decision-making was
+found to be necessary to achieve robust performance of scheduling algorithms,
+as first described in previous work \cite{pdpta18}. Furthermore we have
+demonstrated the use of partial feedback to be insufficient at achieving
+similar robustness, but have proposed the use of biasing the model parameters
+to prevent or reduce the likelihood of the model underestimating task
+requirements thereby modeling tasks as completing earlier than their actual
+completion. Three biasing strategies were proposed, each with different
+assumptions of what knowledge is available about the error inherent in the
+model and different tradeoffs of balancing the amout of overestimation vs.
+likelihood of underestimation of task requirements.  Through simulated case
+studies we demonstrated that each biasing strategy is useful for achieving
+robustness of scheduling algorithm performance at different amount of model
+error.
 

### 2019-05-02 paper.tex
Wordsmith description of proportionate bias strategy results and conclusion/future work section.  Use IEEEtran bibstyle

@@
 in the case of $5\%$ error with no feedback and ideal bias value $P=5\%$.
-In the case of Figure \ref{fig:nofeedback-pbias-mederror} and proportionate
-bias strategy all four scheduling algorithms complete about one third fewer
-workflows at a normalized tardiness of $-0.25$ and below although most of those
-workflows are instead completed at normalized tardiness up to $0$, so they are
-still completed before their deadline.  CMSA with both cost functions completes
+For the proportionate bias strategy, all four scheduling algorithms complete
+about one third fewer workflows at a normalized tardiness of $-0.25$ and below
+although most of those workflows are completed at normalized tardiness up to
+$0$, which is still before their deadline.  CMSA with both cost functions completes
 a few more workflows mildly late (normalized tardiness $0.25$ and below), PLLF
@@
 requirements thereby modeling tasks as completing earlier than their actual
-completion. Three biasing strategies were proposed, each with different
-assumptions of what knowledge is available about the error inherent in the
-model and different tradeoffs of balancing the amout of overestimation vs.
-likelihood of underestimation of task requirements.  Through simulated case
-studies we demonstrated that each biasing strategy is useful for achieving
-robustness of scheduling algorithm performance at different amount of model
-error.
+completion. Three biasing strategies were proposed with unique trade-offs
+of assumed knowledge about error bounds and degree to which they decrease
+underestimation and increase overestimation of task requirements. Through
+simulated case studies we demonstrated that each biasing strategy is useful
+for achieving robustness of scheduling algorithm performance at different
+amounts of model error.
 
-Future work that remains includes analysis of whether the combination of
-partial feedback with any of the biasing strategies can achieve greater
-robustness.  Additionally, other biasing strategies or alternatives to
+Future work may include combination of partial feedback with biasing
+strategies.  Additionally, other biasing strategies or alternatives to
 biasing will be explored to increase robustness or address cases where
-the amount of error in the model is unknown.  Finally, the use of more
-sophisticated approaches such as machine learning may be applied to either
-supplement or replace feedback information from the actual platform.
+the amount of error in the model is unknown.
 
+\bibliographystyle{IEEEtran}
 \bibliography{paper}{}
-\bibliographystyle{unsrt}
 

### 2019-05-29 paper.tex
Dr. Antonio edits.

@@
 \usepackage{caption}
-\usepackage{flushend}
+%\usepackage{flushend}
 
@@
 
-\title{\bf Enhancing Scheduling Robustness with Task Completion Feedback and
-Resource Requirement Biasing}
+\title{\bf Enhancing Scheduling Robustness with Partial Task Completion
+Feedback and Resource Requirement Biasing}
 
@@
 School of Computer Science, University of Oklahoma, Norman, Oklahoma, United States of America\\
+Research Paper
 }
@@
 system into the algorithms' model of the system was crucial for achieving
-robustness.  In the present, various degrees of feedback, rather than simply
-all-or-none, are evaluated using the same simulated studies as in previous
-work and a proposed strategy for biasing model tasks' information is proposed
-in order to counteract the most egregious effects of model error on
-performance.
+robustness.  In the present paper, various degrees of feedback, rather than
+simply all-or-none, are evaluated using the same simulated studies as in
+previous work and a proposed strategy for biasing model tasks' resource
+requirement information is proposed in order to counteract the most egregious
+effects of model error on performance.
 \end{abstract}
@@
 
-Conversely, this paper addresses dynamic scheduling in which the schedule for
-tasks is determined online in real-time with the execution of those tasks on a
-distributed system. Unlike the static scheduling problem, dynamic scheduling
+This paper addresses dynamic scheduling in which the schedule for
+tasks is determined online in real-time with the execution of those tasks
+performed on a distributed system. Unlike static scheduling, dynamic scheduling
 does not require upfront knowledge of the arrival of future tasks into the
@@
 In the present work, multiple tasks may be executed concurrently on a single
+machine. This adds complexity in modeling the machines' performance because
+the machines' resources must be shared across multiple tasks assigned to the
 machine.
 
-Algorithms for dynamic scheduling may be based on heuristics for selecting
+Some algorithms for dynamic scheduling are based on heuristics for selecting
 which tasks to prioritize and determining when to begin their execution and on
@@
 algorithms are generally measured and compared to one another against such
-objectives such as minimizing makespan (time required for completed execution
+objectives as minimizing makespan (time required for completed execution
 of all tasks) \cite{stochastic}, or, as in this paper, the degree to which all
@@
 substantially improve robustness of all four scheduling algorithms even with
-large amounts of error.
+large amounts of error. In the present paper we generalize this approach by
+investigating the utility of using only partial feedback of task completion
+events.
 
@@
 \ref{sec:Framework} describes the problem domain and the simulation software's
-use of modeling the distributed system in which errors in task requirements may
+modeling of a distributed system in which errors in task requirements may
 be present.  Section \ref{sec:Biasing} presents a requirements biasing approach
 to counteracting model error to prevent scheduling algorithms from
-over-committing system resources to executing too many tasks concurrently.
+over-committing system resources, i.e., executing too many tasks concurrently.
 Section \ref{sec:Results} presents results of simulated case studies.
@@
 
-Scheduling algorithms are used to determine \textemdash from a given queue of tasks
-ready to begin executing (i.e. tasks of arrived workflows that have no
+Scheduling algorithms are used to determine \textemdash\ from a given queue of tasks
+ready to begin executing (i.e., tasks of arrived workflows that have no
 precedence constraints or whose precedent tasks have all completed)
-\textemdash both when the task should begin executing and on which machine of
+\textemdash\ both when the task should begin executing and on which machine of
 the platform. Unlike some scheduling research, tasks are permitted to executed
@@
 required number of CPU cycles, and memory load) may contain errors relative to
-the true values of those tasks; these errors then cause the model platform to
+the true values; these errors then cause the model platform to
 diverge from the actual platform in terms of which tasks are completed and
@@
 
-All four studied scheduling algorithms were shown to be sensitive to
+All four studied scheduling algorithms were previously shown to be sensitive to
 even small amounts of error in modeled tasks \cite{pdpta18}.  Each scheduling
@@
 algorithms, even for errors up to 90\% (the highest amount studied) in the
-modeled tasks' requirement for amount of work in CPU cycles.  Figure
+modeled tasks' requirement for amount of work, measured in CPU cycles.  Figure
 \ref{fig:underestimating} illustrates why the model platform's underestimation
@@
 	\end{center}
-	\caption{Illustrating the disconnect due to error such that model task
+	\caption{Illustrating the disconnect due to error, assuming model task
 		requirements underestimate actual task requirements and the model
@@
 In Figure \ref{fig:underestimating} two tasks, $t_1$ and $t_2$, both have
-the same amount of CPU cycles, $C$, required for their completion.  In the
-top half is the modeled platform's view of time in which task $t_1$ begins
+the same amount of CPU cycles, $C$, required for their completion.  The upper
+chart illustrates the modeled platform's view of time in which task $t_1$ begins
 executing first and when it completed, $t_2$ is scheduled to immediately
-begin executing.  However, because the modeled requirements of $t_1$ were
+begin executing.  However, assuming the modeled requirements of $t_1$ were
 an underestimate of the actual $t_1$'s requirements, when the model of
@@
 completion from the actual platform, the modeled completion times of tasks
-may be safely ignored.  However, complete feedback of all tasks' completion
+may be safely ignored, in favor of relying on task completion notifications
+from the actual platform.  However, complete feedback of all tasks' completion
 may be impractical in a live system, or may simply be cost-prohibitive.
 This paper thus seeks to address the question of whether partial feedback
-of tasks' completion times may be sufficient to achieve some level of
+of tasks' completion events may be sufficient to achieve some level of
 robustness to model error.  In addition, based specifically on the knowledge
@@
 scheduling algorithms may schedule future tasks to begin executing
-unintentionally-concurrent with other tasks, delaying their completion.
+unintentionally-concurrent with other tasks, delaying their completions.
 However, if the model is known to have error which may underestimate task
@@
 eliminate) the probability that it underestimates the actual task requirements.
-In this section three proposed strategies for biasing model task requirements
-are proposed.
+In this section three proposed strategies for biasing task requirements are
+proposed.
 
@@
 A more realistic approach to biasing model task requirements is to assume a
-bound, not on the magnitude of error, but on the fraction or percentage of
+bound, not on the magnitude of error, but on the fraction (or percentage) of
 error. It may be possible, for example, through analysis of past executions of
@@
 other words it may be practical to estimate that each model task requirement is
-within $P\%$ of the actual task requirement.  Although that implies $\hat{X}$
-may under- or overestimate $X$ by as much as $P\%$, in order to prevent
+within a factor of $P$ of the actual task requirement.  Although that implies $\hat{X}$
+may under- or over-estimate $X$ by as much as $P$, in order to prevent
 underestimating we can adjust $\hat{X}$ as in Eq. \ref{eq:pbias}, hereafter
@@
 \begin{equation}
-\hat{X^b} \xleftarrow{p} \hat{X} / (1 - P\%)
+\hat{X^b} \xleftarrow{p} \hat{X} / (1 - P)
 \label{eq:pbias}
@@
 Although the proportionate bias strategy can effectively eliminate
-underestimated model task requirements with a judiciously chosen $P\%$
+underestimated model task requirements with a judiciously chosen $P$
 which may require less knowledge about the nature of the error than choosing
@@
 	\caption{Illustration of probabilities for a model task requirement
-		with bound error as a percentage, $P$, of the actual task
+		with bound error as a fraction, $P$, of the actual task
 		requirement, $X$, and the effect of constant and proportionate
@@
 \ref{eq:sbias}. This third strategy fails to eliminate the possibility of
-underestimating though it does reduce its propability substantially, but also
+underestimating though it can reduce its propability substantially, but also
 prevents wildly overestimating task requirements by decreasing the amount of
@@
 \begin{equation}
-\hat{X^b} \xleftarrow{s} \hat{X} (1 + P\%)
+\hat{X^b} \xleftarrow{s} \hat{X} (1 + P)
 \label{eq:sbias}
@@
 	\caption{Illustration of probabilities for a model task requirement
-		with bound error as a percentage, $P$, of the actual task
+		with bound error as a fraction, $P$, of the actual task
 		requirement, $X$, and the effect of the simple bias strategy
@@
 All results were collected using simulations performed using simulator software
-developed for previous research \cite{costmin} and \cite{pdpta18} and made
+developed for previous research \cite{pdpta18} and \cite{costmin} and made
 publically available as open source \cite{soasim}.  Workflows and task
@@
 an averaged value across ten simulations where the workflows and tasks were
-identical but a error term applied to model tasks' requirements were unique.
+identical but an error term applied to model tasks' requirements were unique.
 
@@
 		underestimated task requirements, allowed to model tasks as completing
-		and subsequenting scheduling algorithms allowed to schedule additional
-		tasks to the machine.}
+		and, as a result, scheduling algorithms were allowed to schedule
+		additional tasks to the machine.}
 	\label{fig:noloss-nobias-lowerror}
@@
 actual platform but the model platform is still allowed to model tasks as
-completing early due to underestimates of task requirements. In this figure
+completing early due to underestimates of task requirements. (In other words,
+the model platform only utilizes actual completion events when they occur
+before modeled completion events.)  In this figure
 as with prior research, performance is depicted visually as a histogram of the
@@
 
-Therefore, with any level of partial feedback available it is unexpected that
-any of these scheduling algorithms would perform better than the case of
+Therefore, with any level of partial feedback available none of these
+scheduling algorithms would perform better than the case of
 complete feedback being available but still allowing modeling of early task
@@
 although most of those workflows are completed at normalized tardiness up to
-$0$, which is still before their deadline.  CMSA with both cost functions completes
+zero, which is still before their deadline.  CMSA with both cost functions completes
 a few more workflows mildly late (normalized tardiness $0.25$ and below), PLLF
